\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.84]{geometry}
\nopagenumbers{}
\setlength{\hintscolumnwidth}{2.2cm}

\name{Srikrishnaa}{Vadivel}
\title{Embedded Systems Engineer | FPGA | Robotics | Sensor Logging}
\email{srikrishnaacareers@gmail.com}
\phone[mobile]{516-853-5663}
\social[github]{krishnaa423}
\extrainfo{\href{https://leetcode.com/u/krishnaa42342}{leetcode.com/u/krishnaa42342} \textbar{} \href{https://hub.docker.com/u/krishnaa42342}{hub.docker.com/u/krishnaa42342}}

\begin{document}
\makecvtitle

\section{Profile}
\cvitem{}{Embedded systems engineer with field-tested sensor logging, MCU firmware, FPGA logic, robotics, and scientific instrumentation experience. Comfortable from oscilloscope validation and low-level C through host-side visualization and data systems.}

\section{Experience}
\cventry{2019--2021}{Software and Embedded Engineer}{Probe Technologies / Weatherford}{}{}{\begin{itemize}%
\item Programmed C8051-class microcontrollers and Lattice FPGA logic for sensor logging in geological well tools.
\item Validated embedded systems with oscilloscopes, bench instrumentation, and field deployments.
\item Built host-side CUDA/OpenGL software for large acoustic waveform processing and visualization.
\end{itemize}}
\cventry{2021--present}{Embedded Systems Teaching Assistant / PhD Researcher}{Yale University}{}{}{\begin{itemize}%
\item Served as embedded systems TA while pursuing PhD research in computational materials and scientific computing.
\item Used Linux, C/C++, Python, MPI/OpenMP, PETSc/SLEPc, and HPC systems for simulation workflows.
\end{itemize}}
\cventry{2017}{Robotics Hand Project}{Cornell ECE}{}{}{\begin{itemize}%
\item Built an embedded robotic hand project later published in Circuit Cellar.
\end{itemize}}

\section{Portfolio Projects}
\cvitem{MIPS Processor}{Verilog single-cycle CPU and self-checking Icarus Verilog test bench.}
\cvitem{Matrix-Multiply Accelerator}{Small AI accelerator block with start/done handshake and test bench.}
\cvitem{ROS 2 TurtleBot Simulation}{Robotics simulation plan with trajectory analysis artifacts.}

\section{Education}
\cventry{2021--present}{PhD, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MPhil, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MS, Electrical Engineering}{Yale University}{}{}{}
\cventry{2017--2018}{MEng, Electrical and Computer Engineering}{Cornell University}{}{}{}
\cventry{2013--2017}{BA, Electrical and Computer Engineering}{Cornell University}{}{}{}

\section{Skills}
\cvitem{Programming}{C, C++, Python, Git}
\cvitem{Hardware}{Verilog/SystemVerilog, FPGA, MCU firmware, ADC logging}
\cvitem{Interfaces}{SPI, I2C, UART}
\cvitem{Validation}{Oscilloscopes, bench instrumentation}
\cvitem{Systems}{Linux, CUDA, OpenGL, FreeRTOS concepts}

\end{document}
