\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.84]{geometry}
\nopagenumbers{}
\setlength{\hintscolumnwidth}{2.2cm}

\name{Srikrishnaa}{Vadivel}
\title{Software Engineer | Scientific Computing | Distributed Systems}
\email{srikrishnaacareers@gmail.com}
\phone[mobile]{516-853-5663}
\social[github]{krishnaa423}
\extrainfo{\href{https://leetcode.com/u/krishnaa42342}{leetcode.com/u/krishnaa42342} \textbar{} \href{https://hub.docker.com/u/krishnaa42342}{hub.docker.com/u/krishnaa42342}}

\begin{document}
\makecvtitle

\section{Profile}
\cvitem{}{Software engineer and Yale PhD researcher building scientific computing, high-performance simulation, data visualization, and ML infrastructure. Strong background in Python, C/C++, Linux, CUDA/OpenGL, MPI/OpenMP, Docker, Kubernetes, and production engineering for embedded and server-side systems.}

\section{Experience}
\cventry{2021--present}{PhD Researcher}{Yale University}{}{}{\begin{itemize}%
\item Built first-principles workflows for self-trapped excitons using HPC resources at Oak Ridge, Aurora, LBNL, and LLNL.
\item Developed Python/C++ automation around PETSc/SLEPc, MPI, OpenMP, CMake, Linux shell tooling, containers, and parallel job execution.
\item Prototyped ML models for molecular and materials data, including EGNN force models and diffusion-style generative workflows.
\end{itemize}}
\cventry{2019--2021}{Software and Embedded Engineer}{Probe Technologies / Weatherford}{}{}{\begin{itemize}%
\item Wrote ASP server and Microsoft database tooling for field data systems.
\item Built CUDA/OpenGL acoustic logging visualization software for processing and displaying large waveform data sets.
\item Delivered embedded firmware for C8051-class MCUs and Lattice FPGA sensor logging used in geological well tools; validated with oscilloscopes and field tests.
\end{itemize}}
\cventry{2018--2019}{Photonics Blogger}{FindLight}{}{}{\begin{itemize}%
\item Wrote technical photonics articles translating optics products and applications into clear engineering content.
\end{itemize}}

\section{Projects}
\cvitem{DOLFINx PDE Gallery}{Weak-form derivations, Poisson solver, PyVista visualization, and documentation in index notation.}
\cvitem{Meep Ring Resonator}{FDTD photonics simulation of a ring coupled to a waveguide with field animation workflow.}
\cvitem{First-Principles LiF}{Plane-wave Hamiltonian scaffold and band plotting for DFT-style workflows.}
\cvitem{ROS 2 TurtleBot Simulation}{Docker-oriented Nav2/Gazebo plan with trajectory analysis fallback.}

\section{Education}
\cventry{2021--present}{PhD, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MPhil, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MS, Electrical Engineering}{Yale University}{}{}{}
\cventry{2017--2018}{MEng, Electrical and Computer Engineering}{Cornell University}{}{}{}
\cventry{2013--2017}{BA, Electrical and Computer Engineering}{Cornell University}{}{}{}

\section{Skills}
\cvitem{Languages}{Python, C, C++, Bash, SQL}
\cvitem{Systems}{Linux, CMake, Docker, Kubernetes, MPI, OpenMP}
\cvitem{Scientific / ML}{PETSc, SLEPc, PyTorch, NumPy, SciPy, pandas, scikit-learn, Hugging Face}
\cvitem{Platforms}{CUDA, OpenGL, AWS, GCP, Terraform}

\end{document}
