\documentclass[10pt,letterpaper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\usepackage[scale=0.84]{geometry}
\nopagenumbers{}
\setlength{\hintscolumnwidth}{2.2cm}

\name{Srikrishnaa}{Vadivel}
\title{Electrical Engineer | Photonics | Embedded Systems | Scientific Computing}
\email{srikrishnaacareers@gmail.com}
\phone[mobile]{516-853-5663}
\social[github]{krishnaa423}
\extrainfo{\href{https://leetcode.com/u/krishnaa42342}{leetcode.com/u/krishnaa42342} \textbar{} \href{https://hub.docker.com/u/krishnaa42342}{hub.docker.com/u/krishnaa42342}}

\begin{document}
\makecvtitle

\section{Profile}
\cvitem{}{Electrical engineer with Cornell ECE training, photonics communication, embedded systems delivery, FPGA/MCU experience, and current Yale PhD work in computational materials and high-performance scientific software.}

\section{Experience}
\cventry{2021--present}{PhD Researcher / Embedded Systems TA}{Yale University}{}{}{\begin{itemize}%
\item Research first-principles self-trapped excitons using HPC systems and scientific software stacks.
\item Teach and support embedded systems concepts spanning firmware, instrumentation, and debugging.
\end{itemize}}
\cventry{2019--2021}{Software and Embedded Engineer}{Probe Technologies / Weatherford}{}{}{\begin{itemize}%
\item Developed embedded sensor logging firmware and Lattice FPGA logic for geological well tools.
\item Built CUDA/OpenGL acoustic waveform processing and visualization tooling.
\item Contributed ASP and Microsoft database software for field data workflows.
\end{itemize}}
\cventry{2018--2019}{Photonics Blogger}{FindLight}{}{}{\begin{itemize}%
\item Wrote clear technical content on photonics products, optics, and applications.
\end{itemize}}

\section{Projects}
\cvitem{Digital Design}{Verilog MIPS CPU and matrix-multiply accelerator with Icarus test benches.}
\cvitem{Photonics}{Meep ring resonator FDTD model for integrated photonics simulation.}
\cvitem{Numerics}{DOLFINx PDE notes and solver scaffold for finite-element methods.}
\cvitem{Robotics}{Embedded robotic hand project published in Circuit Cellar.}

\section{Education}
\cventry{2021--present}{PhD, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MPhil, Electrical Engineering}{Yale University}{}{}{}
\cventry{2023}{MS, Electrical Engineering}{Yale University}{}{}{}
\cventry{2017--2018}{MEng, Electrical and Computer Engineering}{Cornell University}{}{}{}
\cventry{2013--2017}{BA, Electrical and Computer Engineering}{Cornell University}{}{}{}

\section{Skills}
\cvitem{Core}{Circuits, embedded C, Verilog, FPGA, MCUs, signal processing}
\cvitem{Photonics}{Photonics, optics communication}
\cvitem{Software}{Python, C++, Linux, OpenGL, CUDA}
\cvitem{Scientific}{HPC, numerical methods}

\end{document}
